\section{Previous Years}
%This section briefly describes the projects developed for the \ac{giraf} project during 2011 and 2012.

During the first year of development, four parts of the \ac{giraf} project were developed. The four projects were developed during the spring semester of 2011 and included the projects:
\begin{description}
\item [Admin] An administration interface used for administrating different aspects of the \ac{giraf} system.
\item [DigiPECS] A digitized version of ``Picture Exchange Communication System''\cite{pecs} a system used as an aid for communication with people with special needs such as autism.
\item [Launcher] A home screen application and distribution platform for Android.
\item [aSchedule] A visual schedule for the Android platform.
\end{description}

During the spring semester of 2012, five new software groups continued development of the \ac{giraf} project. The projects developed during 2012 were:

\begin{description}
\item [Launcher] An enhancement of the launcher project developed during the spring semester of 2011.
\item [Oasis] An enhancement of the admin project from 2011. Furthermore the Oasis project developed a local database for the \ac{giraf} system.
\item [Parrot] An enhancement of the DigiPECS project from 2011. The project was renamed because of trademark issues.
\item [Savannah] A server side database with web interface for the \ac{giraf} system.
\item [Wombat] An Android application for measuring and visualizing time.
\end{description}

%During the spring semester of 2012, two different projects working with databases were developed although the databases from the two projects were never made able to synchronize.
During the spring semester of 2012 two databases were developed, however synchronization between them was never achieved.

\subsection*{Problems with Initial Implementation}
As the spring semester of 2013 started, an ''install party'' for the students was held. The party was intended to help the students compile and deploy the projects from 2012.

Even though a representative for each of the 2012 groups were present, some compilation problems still occurred.

The repository used for distributing in 2012, was disorganized and difficult to navigate, i.e. due to:
\begin{itemize}
  \item Multiple copies of the same project.
  \item Unclear dependencies among the different projects.
  \item Projects only meant to be compiled from Eclipse for Windows.
\end{itemize}

During the following week a working workspace was created and shared with the rest of the students, along with install instructions. The install instructions were later updated to a more clear edition.
